Cultural Transmission Can Explain the Evolution of Cooperation

### 2020-08-15 ms/main.tex
Update figure 2

\begin{figure}[htb]
  \centering
    \includegraphics[scale=1]{figure2a.pdf}
    \includegraphics[scale=1]{figure2b.pdf}
  \caption{\textbf{Vertical and horizontal transmission.} The figure illustrates combinations of horizontal bias, $T_A-T_B$, and cost of cooperation, $c$, that lead to either global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial frequencies (blue), or coexistence of cooperation and defection (yellow). The blue and orange curves show the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}).
  Here, benefit of cooperation is $b=1.3$, horizontal transmission of cooperation $T_A=0.4$, $c$ and $T_B$ vary on the y- and x-axes. \textbf{Up}: With $\alpha = 0.7 > 0$, coexistence is possible (yellow). \textbf{Down}: With $\alpha=0$, coexistence is not possible.}
    \label{fig:results2}
\end{figure}
%%%

>>>>

\begin{figure}[htb]
  \centering
    \includegraphics[scale=0.75]{figure2a.pdf}
    \includegraphics[scale=0.7]{figure2b.pdf}
    \includegraphics[scale=0.7]{boundiries_withAlpha_y_axis.pdf}
    \caption{\textbf{Vertical and horizontal transmission.} The figure illustrates (\textbf{a-b}): combinations of horizontal bias, $T_A-T_B$, and cost of cooperation, $c$; (\textbf{c}) combinations of horizontal bias, $T_A-T_B$, and probability of horizontal transmission with social partner, $alpha$, that lead to either global fixation of cooperation (green), global fixation of defection (red), fixation of either cooperation or defection depending on the initial frequencies (blue), or coexistence of cooperation and defection (yellow). 
    In (\textbf{a-b}): the blue and orange curves show the cost boundaries $\gamma_1$ and $\gamma_2$ (\autoref{eq:cost_boundaries}).
  Here, benefit of cooperation is $b=1.3$, horizontal transmission of cooperation $T_A=0.4$, (\textbf{a-b}): $c$ and $T_B$ vary on the y- and x-axes; (\textbf{c}): $\alpha$ and $T_B$ vary on the y- and x-axes.
   (\textbf{a}): With $\alpha = 0.7 > 0$, coexistence is possible (yellow). (\textbf{b}): With $\alpha=0$, coexistence is not possible. (\textbf{c}): with $c = 0.35$ coexistence is possible.}
    \label{fig:results2}
\end{figure}
%%%
